% $Id: introduction.tex 87303 2016-02-08 13:44:29Z lafferty $
\clearpage
\newpage
\section{Appendix: Normalization}
\label{app:normalization}

The signal yield is normalised with respect to \Kspipi . The yield is computed as follows:
\begin{equation}
N(\KsPzMuMu) = \sigma(\PKzS){\cal B}(\KsPzMuMu)\epsilon_{\KsPzMuMu} L,
\end{equation}
where $\sigma(\PKzS)$ is the \KS production cross-section, $\epsilon_{\KsPzMuMu}$ the absolute efficiency and $L$ the integrated luminosity. Taking the ratio of N(\KsPzMuMu) with respect to N(\Kspipi), both the 
cross-section and the luminosity get cancelled out, leading to the formula:

\begin{equation}
\frac{N(\KsPzMuMu)}{N(\Kspipi)} = \frac{\BRof\KsPzMuMu}{\BRof\Kspipi} \frac{\epsilon_{\KsPzMuMu}}{\epsilon_{\PKzS\to\Pgpp\Pgpm}}.
\end{equation}

The effective luminosity, $L^{dat}_{eff}$, is calculated according to

\begin{equation}
L^{dat}_{eff} = \epsilon^{TIS}_{\Kspipi}L^{dat}, \\
\end{equation}	
where $\epsilon_{TIS}(\Kspipi)$ is the TIS efficiency calulated using \Kspipi events and $L^{dat}$ is the luminosity used for the fit to the data.

\begin{eqnarray}
L^{FULL,2011}_{eff} &=& 0.0016 \cdot 992\;\rm pb^{-1} = 1.59\;\invpb, \\
L^{FULL,2012}_{eff} &=& 0.0016 \cdot 2037\;\rm pb^{-1} = 3.26\;\invpb,\\
L^{PARTIAL}_{eff} &=& 0.0025 \cdot 306\;\rm pb^{-1} = 0.77\;\invpb. 
\end{eqnarray}

The offline signal efficiency (or, equivalently, the total efficiency for a $100\%$ efficient trigger) for the FULL channel is calculated as follows:
\begin{itemize}

\item The generator level efficiency is estimated to be $0.361$. 
\item The efficiency of the FULL stripping on generated events is $1.84$ per mil according to the statistics produced by the DaVinci filtering script. This number has to be corrected by the fact that $3.3\%$ of the events didn't actually contain a signal candidate at all \footnote{In a fraction of events, the information on how the \KS should decay is lost as the particle is passed to GEANT4.}. It also has to be corrected by the fact that some of the selected candidates aren't matched to the signal. After this corrections, it becomes $1.79$ per mil.
\item The efficiency of the fiducial cuts  and mass fit window are $0.931$ and $0.922$. These are applied prior to BDT training.
\end{itemize}

The offline signal efficiency (or, equivalently, the total efficiency for a $100\%$ efficient trigger) for the PARTIAL channel is calculated as follows:
\begin{itemize}

\item The generator level efficiency is estimated to be $0.361$. 
\item The efficiency of the PARTIAL stripping on generated events, calculated in the same way as above is $1.23\%$.
\item The efficiency of the fiducial cuts  and mass fit window are $0.734$ and $0.917$ respectively. These are applied prior to BDT training.
\end{itemize}
